Data dictionary

### 2023-07-26 _data-dictionary.qmd
Built site for gh-pages

---
title: "Cognate beginnings to bilingual lexical acquisition"
subtitle: "Lab notes"
short-title: "Cognate beginnings"
author:
  - name: Gonzalo Garcia-Castro
    corresponding: true
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    affiliations:
      - id: cbc
        name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        address: Ramon Trias Fargas 25-27
        city: Barcelona
        region: Spain
        postal-code: "08005"
  - name: Daniela S. Avila-Varela
    orcid: 0000-0002-3518-8117
    affiliations: 
      - ref: cbc
      - id: ul
        name: Universidade de Lisboa
        department: Facultade de Letras
        address: Alameda da Universidade
        city: Lisboa
        region: Portugal
        postal-code: "1600-214"
  - name: Ignacio Castillejo
    orcid: 0000-0001-7445-0416
    affiliations: 
      - id: uam 
        name: Universidad Autónoma de Madrid
        department: Departamento de Psicología
        address: Iván Pavlov, 6
        city: Madrid
        region: Spain
        postal-code: "28049"
  - name: Nuria Sebastian-Galles
    orcid: 0000-0001-6938-2498
    affiliations: 
      - ref: cbc
date: last-updated
code-repo: "Access the code, data, and analysis at <https://github.com/gongcastro/trajectories>"
keywords:
  - lexical acquisition
  - vocabulary
  - bilingualism
  - item response theory
  - bayesian
link-citations: true
editor: source
code-fold: true
warning: false
error: false
format:
  html:
    theme: _assets/style.scss

toc: true
fig-dpi: 1000
---

@@

::: callout-tip
Data and materials are available at [OSF](https://osf.io/hy984/), and code is available at [GitHub](https://github.com/gongcastro/trajectories), and [Docker](https://hub.docker.com/r/gongcastro/cognate-beginnings).
:::

## Abstract

`r abstract`

## Acknowledgements

`r thanks`

{{< include ../README.md >}}

# Data dictionaries

::: {.tabset-panel}

@@

```{r items}
items |>
    head(15)
```

@@

```{r participants}
participants |>
    head(15)
```

@@

```{r responses}
responses |>
    head(15)
```

@@

# Session info

```{r}
sessionInfo()
```

>>>>

---
title: Data dictionary
---

@@

::: {.panel-tabset}

@@

```{r items}
items |>
    head(10) |>
    knitr::kable(digits = 2)
```

@@

```{r participants}
participants |>
    head(10) |>
    knitr::kable(digits = 2)
```

@@

```{r responses}
responses |>
    head(10) |>
    knitr::kable(digits = 2)
```

@@
